Empirical normative theories

### 2020-08-05 simple.tex
One more example of a theory: satisfying

\begin{abstract}
	TODO
\end{abstract}

\section{Motivation}

@@

\section{LS}
%Idea: argue for P > $.
%4 ways:
%- choose
%- rate attractivity: b1 → +; b2 → ++ thus b2 > b1
%- bids to buy (B-bid): I’d pay max $4 to buy and play b1; I’d pay max $6 to play b2 thus b2 > b1
%- bids to sell (S-bid): I’d sell b1 for at least $3; I’d sell b2 for at least $5 thus b2 > b1.
%
%First two: focus on probs. Last two: focus on amounts.
%
%Compare P = (.99, +$4; .01, −$0.1) VS $ = (.33, +$16; .67, −$2). Typically, choose P and bid more for $.
%E[P] ≈ $4; E[$] ≈ 5+1/3 − 4/3 = $4.
%
%XP1. Choice VS S-bid. No gambling. 6 P bets, 7 $ bets. 12 pairs, of which 6 presented in the table: (P, $), choose one, and indicate the strength of your preference (slight to very strong). Then 19 bets using S-big, 6 practice (other bets) then 13 were analyzed.
%
%E[P] and E[$] (of the example above) are similar, but bids “greatly exceeding the expected value of $3.94 are common”.
%
%XP2. Choice VS B-bid.
%
%XP3. With effective gambling and iterated thinking to thing about their preference.
Define $P = (.99, +\$4; .01, −\$0.1)$ and $D = (.33, +\$16; .67, −\$2)$.

@@

TODO consider using only $\phi$ being sure, and dropping everything related to possibility.

>>>>

\begin{abstract}
	TODO: abstract
\end{abstract}

\section{Motivation}
Talk about \citet{von_neumann_theory_2004}.

@@

\section{Preferences}
\subsection{Preferences}
Let $\allalts$ be a set of alternatives. Define $\Phi_\allalts$ as follows. Let $\phi_{a > b} \in \iPhi$ represent $i$ deliberately preferring strictly $a$ to $b$. Let $\phi_{a ≥ b} \in \iPhi$ represent $i$ deliberately preferring weakly $a$ to $b$. Define $¬\phi_{a > b} = \phi_{b ≥ a}$.

A normative theory of preferences about $\allalts$ is a theory about $\Phi_\allalts$: a tuple $(\allprops, ¬, \allargs, I, (\ileadsto)_{i \in I})$, with $\allprops$ defined as $\allprops_\allalts$, $¬$ defined as above.

Define $≥_i$, the deliberated preference of $i$, as $a ≥_i b$ iff $\phi_{a ≥ b} \in \iPhi$.

Given an empirical theory for a normative theory of preferences, say that it claims a complete preference iff $\forall a, b \in \allalts: \phi_{a ≥ b} \in \gPhi \lor \phi_{b ≥ a} \in \gPhi$. Similarly, it claims a transitive preference iff $\forall a, b, c \in \allalts: \phi_{a ≥ b} \in \gPhi \land \phi_{b ≥ c} \in \gPhi ⇒ \phi_{a ≥ c} \in \gPhi$. Observe that establishing whether an empirical theory claims a complete or transitive preference can be determined a priori (without empirical observations).

Given a bundle $B \subseteq \allalts$ and $i \in I$, $b \in B$ is a deliberated preferred choice for $i$ among $B$ iff $\forall b' \in B: b ≥_i b'$.

The next result follows from these definitions and from classical results about choice functions and complete, transitive preferences. \TODO{Be more precise.}
 \begin{theorem}
 	If an empirical theory for a normatively adequate normative theory of preference claims a complete and transitive preference and is valid, then, given any bundle $\emptyset ≠ B \subseteq \allalts$, some $b \in B$ is a deliberated preferred choice for $i$ among $B$.
 \end{theorem}

Given $i$ and $\phi_{a > b}$, $\hist \ileadsto \phi$ iff $i$, after having been presented $\ar$, is asked to choose among $a$, $b$, or declare she is indifferent if permitted; and $i$ chooses $a$. And $\hist \ileadsto \phi_{a ≥ b}$ iff $i$ does not choose $b$ (thus chooses $a$ or declare she is indifferent if permitted). Note that $\hist \ileadsto \phi ⇔ \hist \nileadsto ¬\phi$.

\subsection{Satisfaction}
Consider a normative theory of preferences about a given set of alternatives $\allalts$. Let $\gamma$ be the following empirical theory for that normative theory.

Define $C$ a set of criteria, functions $c: \allalts → \R$ measuring the performances of the alternatives according to some point of view. Let $t: \R^C$ be a set of thresholds, thus, consisting of one real threshold $t_c \in \R$ per criterion. Say that $a \in \allalts$ is satisficing iff $\forall c \in C: c(a) ≥ t_c$.

The theory $\gamma$ says that $i$ is a satisficer using some defined criteria $C$ and thresholds $t = (t_c)_{c \in C}$. The set $\gPhi$ is defined as $\set{\phi_{a > b} \suchthat a \text{ is satisficing and $b$ is not}}$. Given $a, b \in \allalts$, with $a$ satisficing and $b$ not, define $\ar_{a > b}$ as the text: “$a$ has performance $c_1(a)$ on criterion $c_1$, and it is reasonable to consider that having at least $t_{c_1}$ is satisfying enough from the point of view captured by $c_1$, (… same phrase for the other criteria…), therefore, it is a fully satisfactory alternative; whereas $b$ is not satisfactory on criteria (… enumeration of the criteria such that $c(b) < t_{c}$).” 
Define ${\gleadsto} = \set{\ar_{a > b}, \phi_{a > b}) \suchthat a \text{ is satisficing and $b$ is not}}$.
Define $\alldargs = \gbeats = \dbeats = {+} = \emptyset$: the theory does not consider any counter-argument as potentially damaging. 
This defines the theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$.

Observe that $\gamma$ does not claim a complete preference, but, whenever there is exactly one satisficing alternative in $\allalts$, it still determines a deliberated preferred choice for $i$ among $\allalts$.

\subsection{LS}
%Idea: argue for P > $.
%4 ways:
%- choose
%- rate attractivity: b1 → +; b2 → ++ thus b2 > b1
%- bids to buy (B-bid): I’d pay max $4 to buy and play b1; I’d pay max $6 to play b2 thus b2 > b1
%- bids to sell (S-bid): I’d sell b1 for at least $3; I’d sell b2 for at least $5 thus b2 > b1.
%
%First two: focus on probs. Last two: focus on amounts.
%
%Compare P = (.99, +$4; .01, −$0.1) VS $ = (.33, +$16; .67, −$2). Typically, choose P and bid more for $.
%E[P] ≈ $4; E[$] ≈ 5+1/3 − 4/3 = $4.
%
%XP1. Choice VS S-bid. No gambling. 6 P bets, 7 $ bets. 12 pairs, of which 6 presented in the table: (P, $), choose one, and indicate the strength of your preference (slight to very strong). Then 19 bets using S-big, 6 practice (other bets) then 13 were analyzed.
%
%E[P] and E[$] (of the example above) are similar, but bids “greatly exceeding the expected value of $3.94 are common”.
%
%XP2. Choice VS B-bid.
%
%XP3. With effective gambling and iterated thinking to thing about their preference.
Define $P = (.99, +\$4; .01, −\$0.1)$ and $D = (.33, +\$16; .67, −\$2)$.

@@

\TODO{Consider using only $\phi$ being sure, and dropping everything related to possibility.}
